Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-11-28 paper/main.tex
exchange order
fixup! rewrite text for benchmarking extraction algorithm

In order to quantitatively analyze this disparity we use both data to calculate the average rod
length of the bacteria (Figure~\ref{fig:benchmarking-extraction-algorithm} (J)) over the course of
the simulated time interval.
The results show good agreement with larger discrepancies directly after division events.
In addition figure~\ref{fig:benchmarking-extraction-algorithm} (K) displays individual displacements
of exact and extracted vertices which have been reoriented with respect to the direction of the rod.
Values closer to the center represent better agreement.
The distribution of these displacements can be well described by a normal distribution with mean
$\mu$ and variance $\sigma$.
These parameters can be obtained by fitting the distribution to the displacements at every time
point which is displayed in Figure~\ref{fig:benchmarking-extraction-algorithm}.
Here we can also see that the overall variance in the displacements increases directly after
division events.
However, the center of the distributions remain concentrated near zero without significant outliers
which demonstrates the robustness of our method in these densely packed scenarios.
Further details are given in the supplementary
materialsec:supsec:supplement-imaging-based-comparison-algorithm-details
(section~\ref{sec:supplement-imaging-based-comparison-algorithm-details}).

@@

\section{Author Contributions}
\textbf{Conceptualization:} Jonas Pleyer\\
\textbf{Investigation:} Jonas Pleyer\\
\textbf{Methodology} Jonas Pleyer\\
\textbf{Software:} Jonas Pleyer\\
\textbf{Supervision:} Christian Fleck\\
\textbf{Writing – original draft:} Jonas Pleyer\\
\textbf{Writing – review \& editing:} Jonas Pleyer \& Christian Fleck

>>>>

In order to quantitatively analyze this disparity we use both data to calculate the average rod
length of the bacteria (Figure~\ref{fig:benchmarking-extraction-algorithm} (J)) over the course of
the simulated time interval.
The results show good agreement with larger discrepancies directly after division events.
In addition figure~\ref{fig:benchmarking-extraction-algorithm} (K) displays individual displacements
of exact and extracted vertices which have been reoriented with respect to the direction of the rod.
Values closer to the center represent better agreement.
The distribution of these displacements can be well described by a normal distribution with mean
$\mu$ and variance $\sigma$.
These parameters can be obtained by fitting the distribution to the displacements at every time
point which is displayed in Figure~\ref{fig:benchmarking-extraction-algorithm}.
Here we can also see that the overall variance in the displacements increases directly after
division events.
However, the center of the distributions remain concentrated near zero without significant outliers
which demonstrates the robustness of our method in these densely packed scenarios.
Further details are given in the supplementary materials
(section~\ref{sec:supplement-imaging-based-comparison-algorithm-details}).

@@

\section{Author Contributions}
\textbf{Conceptualization:} Jonas Pleyer\\
\textbf{Investigation:} Jonas Pleyer\\
\textbf{Methodology} Jonas Pleyer\\
\textbf{Software:} Jonas Pleyer\\
\textbf{Supervision:} Christian Fleck\\
\textbf{Writing – original draft:} Jonas Pleyer\\
\textbf{Writing – review \& editing:} Christian Fleck \& Jonas Pleyer
